Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-01-28 jss/article.tex
Added script to reproduce ACSNMineR paper results
- edit in Pdf plot lines (coherent with script)
- script to:
* show data structure
* compute enrichment
* generate plots

represent_enrichment(enrichment = list(SampleA = enrichment_test[1:10,], 
  SampleB = enrichment_test[3:10,]), plot = "heatmap", scale = "log", 
  low = "steelblue" , high ="white", na.value = "grey")

@@

represent_enrichment(enrichment = list(SampleA = enrichment_test[1:10,],
 SampleB = enrichment_test[3:10,]), plot = "bar", scale = "log", nrow = 1)
\end{verbatim}

>>>>

represent_enrichment(enrichment = list(Corrected = results[1:10,], 
Uncorrected = results_uncorrected[1:10,]),
                                plot = "heatmap", scale = "log", 
                                low = "steelblue" , high ="white", na.value = "grey")

@@

 represent_enrichment(enrichment = list(Corrected = results[1:10,], 
                             Uncorrected = results_uncorrected[1:10,]),
                               plot = "heatmap", scale = "reverselog", 
                               nrow = 1)
\end{verbatim}
